---
title: "Emotionality influences beliefs"
author: "Salonee Jukar & Matti Vuorre"
date: "2025-03-01"
output: pdf_document
---

```{r setup, include=FALSE}
# Load required libraries
library(dplyr)
library(psych)

```



```{r}
#Pre-Test

df<-read.csv2(file.choose(), header=T) #Stimuli_Longform_new downloaded from python and edited to seperate the 3 columns with negative, neutral and positive values
View(df)

df$Negative <- as.numeric(df$Negative)
df$Neutral <- as.numeric(df$Neutral)

# Filter for True (T) and Fake (F) headlines
df_true <- df %>% filter(grepl("T", headline_code))
df_fake <- df %>% filter(grepl("F", headline_code))

# Further split into Emotional (E) and Neutral (N)
df_true_emotional <- df_true %>% filter(grepl("E$", headline_code))
df_true_neutral <- df_true %>% filter(grepl("N$", headline_code))

df_fake_emotional <- df_fake %>% filter(grepl("E$", headline_code))
df_fake_neutral <- df_fake %>% filter(grepl("N$", headline_code))

# Perform independent t-tests on Negative Scores
t_test_true <- t.test(df_true_emotional$Negative, df_true_neutral$Negative)
t_test_fake <- t.test(df_fake_emotional$Negative, df_fake_neutral$Negative)

t_test_true
t_test_fake


# Perform independent t-tests on Neutral Scores
t_test_true_neu <- t.test(df_true_emotional$Neutral, df_true_neutral$Neutral)
t_test_fake_neu <- t.test(df_fake_emotional$Neutral, df_fake_neutral$Neutral)

t_test_true_neu
t_test_fake_neu